Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-03-11 hotstorage13/eval.tex

Figure~\ref{fig:memory} shows the total parallel time in hours to backup 2500 VMs on
 a 100-node cluster a  when 
the memory limit $M$ imposed on each node varies  from 20MB to 200MB.
This figure also depicts the time breakdown for Stages 1, 2, and 3. 
%The parallel time includes the first scanning time, 
%of dirty VM segments to generate block fingerprints, data redistribution for request accumulation,
%fingerprint comparison, duplicate summary distribution, and the second scan time for real backup.
The time in Stages 1 and 2  is  dominated by  the two scans of dirty VM segments
and the time for copying to the final backup storage is overlapped with VM scanning.
During dirty VM segment reading, the average number of consecutive dirty segments is 2.92. 
%Each scan takes about 1.4 hours.
The overall processing time does not have a significant reduction as $M$ increases to 200MB.
The aggregated deduplication throughput is  about 9.6GB per second,
which is the size of 2500 VM images divided by the parallel time. 
The system runs with  a single thread and  its CPU resource usage is upto 10\% of one core. 
The result shows the backup with multi-stage deduplication  for all VM images can be 
completed in about 2.9 hours with 35MB memory,  8GB disk overhead and a small CPU usage.
As we vary the cluster size $p$,  the parallel time does  not change much, and  the aggregated throughput
scales up linearly since the number of VMs is  $25p$.

>>>>

Figure~\ref{fig:memory} shows the total parallel time in hours to backup 2500 VMs on
 a 100-node cluster a  when 
the memory limit $M$ imposed on each node varies  from 20MB to 200MB.
This figure also depicts the time breakdown for Stages 1, 2, and 3. 
%The parallel time includes the first scanning time, 
%of dirty VM segments to generate block fingerprints, data redistribution for request accumulation,
%fingerprint comparison, duplicate summary distribution, and the second scan time for real backup.
The time in Stages 1 and 3  is  dominated by  the two scans of dirty VM segments
and the time for copying to the final backup storage is overlapped with VM scanning.
During dirty VM segment reading, the average number of consecutive dirty segments is 2.92. 
%Each scan takes about 1.4 hours.
The overall processing time does not have a significant reduction as $M$ increases to 200MB.
The aggregated deduplication throughput is  about 9.6GB per second,
which is the size of 2500 VM images divided by the parallel time. 
The system runs with  a single thread and  its CPU resource usage is upto 10\% of one core. 
The result shows the backup with multi-stage deduplication  for all VM images can be 
completed in about 2.9 hours with 35MB memory,  8GB disk overhead and a small CPU usage.
As we vary the cluster size $p$,  the parallel time does  not change much, and  the aggregated throughput
scales up linearly since the number of VMs is  $25p$.
